Transient Variability In Vapor Intrusion And The Factors That Influence It

### 2019-01-23 tex/main.tex
Tmp
Started writing on new paper, adding plots

% additional packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{array,multirow,graphicx}
\usepackage{comment}
\graphicspath{
  {./../figures/},
  {./../figures/air-exchange-rate/},
  {./../figures/kde-iacc-pressure/},
  {./../figures/preferential-pathway-sensitivity/},
  {./../figures/transient-response/},
  {./../figures/multivariate_analysis/},
  {./../figures/rate_of_change/},
}
\usepackage{lineno}
\linenumbers
% macros

@@

@@

>>>>

% additional packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{array,multirow,graphicx}
\usepackage{comment}
\graphicspath{
  {./../figures/},
  {./../figures/air-exchange-rate/},
  {./../figures/kde-iacc-pressure/},
  {./../figures/preferential-pathway-sensitivity/},
  {./../figures/transient-response/},
  {./../figures/multivariate_analysis/}
}
\usepackage{lineno}
\linenumbers
% macros

@@

The significant temporal varibility in indoor air contaminant concentrations at vapor intrusion (VI) sites pose a major impedent for assertaining the relevant human exposure to vapor contaminant.
Exactly how significantly the indoor air concentration may vary, and the causes of the variability is poorly understood.
Improving our understanding of these two factors are crucial to reduce uncertainty in determining indoor air contaminant exposures, and reducing the length of these investigations.

Two well-documentated VI sites both showed significant temporal variability in indoor air contaminant concentrations.
One is a two-story house near Hill AFB in Utah (called the ASU house in this paper), and the other a duplex in Indianapolis, IN.

The discovery of preferential pathways for contaminant entry at VI sites has further

@@

\begin{figure}[htb!]
  \caption{ }
  \label{fig:temporal_variability}
  % ASU/North Island plot
  \begin{subfigure}{0.49\textwidth}
    \centering
    \caption{ }
    \label{fig:temporal_variability_asu}
    \includegraphics[width=\textwidth]{temporal_variability/asu.pdf}
  \end{subfigure}
  % Indianapolis plot
  \begin{subfigure}{0.49\textwidth}
    \centering
    \caption{ }
    \label{fig:temporal_variability_indianapolis}
    \includegraphics[width=\textwidth]{temporal_variability/indianapolis.pdf}
  \end{subfigure}
\end{figure}

\subsection{Maximum Change in Indoor Air Contaminant Concentration}

\begin{figure}[htb!]
  \caption{ }
  \label{fig:resampling}
  \includegraphics[width=\textwidth]{temporal_variability/resampling.pdf}
\end{figure}

\subsubsection{Conclusions From Steady-State Modeling}

\begin{figure}[htb!]
  \caption{Sensitivity analysis of IACC dependence on indoor/outdoor pressure difference for cases featuring a preferential pathway (\ref{fig:ss-sensitivity-analysis-pp}) and without a preferential pathway (\ref{fig:ss-sensitivity-analysis-no-pp}). Results compared with field data from ASU house.}
  \label{fig:ss-sensitivity-analysis}
  % "Overview" plot
  \begin{subfigure}{0.45\textwidth}
    \caption{preferential pathway present. Sensitivity to the presence of a gravel sub-base and contamination in the preferential pathway considered.}
    \label{fig:ss-sensitivity-analysis-pp}
    \includegraphics[width=\textwidth]{yes-pp.pdf}
  \end{subfigure}
  % Violinplot figure
  \begin{subfigure}{0.45\textwidth}
    \caption{No preferential pathway present. Sensitivitiy to the presence of a gravel sub-base considered.}
    \label{fig:ss-sensitivity-analysis-no-pp}
    \includegraphics[width=\textwidth]{no-pp.pdf}
  \end{subfigure}
\end{figure}
